---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
---

# Plotly of Instacart

Instacart data 

```{r}
library(tidyverse)
library("p8105.datasets")
library(plotly)
library(dplyr)
```

## Loading data
```{r, message = FALSE}
data("instacart")

```

## To find whether fruits are reordered more frequently than vegetables. 

```{r, message = FALSE}
instacart_fruits = 
  instacart %>% 
  select(aisle, reordered) %>% 
  filter(
    aisle == "fresh fruits"
  ) %>% 
  count(reordered == "1") %>% 
  knitr::kable()
```

```{r, message = FALSE}
instacart_vegetables = 
  instacart %>% 
  select(aisle, reordered) %>% 
  filter(
    aisle == "fresh vegetables"
  ) %>% 
  count(reordered == "1") %>% 
  knitr::kable()
```

Based on two tables that I made regarding the `reordered` of `fresh fruits` and `fresh vegetables`, it is obvious that the rate of reordering `fresh fruits` is `110782/(110782+39691) = 0.736`; the rate of reordering `fresh vegetables` is `91368/(91368+59241) = 0.607`. Since `0.763 > 0.607` It is true that fruits are reordered more frequently than vegetables. 


## loading data for plots
```{r, message = FALSE}
instacart_new = 
  instacart %>% 
  select(reordered, order_number, days_since_prior_order, product_name, aisle, department, order_hour_of_day, add_to_cart_order) %>% 
  filter(
    reordered == "1",
    days_since_prior_order < 10,
    department == "produce",
    order_number > 25,
   aisle == "fresh vegetables") %>% 
  filter(grepl("Organic", product_name))
  
```
The data that I chose from the instacart are `fresh vegetables` which were reordered and has the `order_number` larger than `25` and belong to the `department` of `produce`. Also, I chose the `fresh vegetabels` which are `organic`. 

## Plotly plots 

# scatterplot 
```{r, message = FALSE}
instacart_new %>% 
  
  plot_ly(x = ~order_number, y = ~add_to_cart_order, color = ~product_name, alpha = .5, type = "scatter", mode = "markers")
```
Here's the scatterplot which show the relationship between `order_numebr` and `add_to_cart_order`. However, there's no direct relationship between `order_numebr` and `add_to_cart_order` of those organic fresh vegetables. 

# Boxplot 

```{r, message = FALSE, fig.width = 10}
instacart_new %>% 
  filter(
    order_number > "90"
  ) %>% 
  mutate(product_name = fct_reorder(product_name, order_number)) %>% 
  plot_ly(y = ~order_number, x = ~product_name, color = ~product_name, type = "box", colors = "viridis", alpha = .5)
```

## Bar plot 

```{r}
instacart_new %>%
  filter(
    order_number > "90"
  ) %>% 
  count(product_name) %>% 
  mutate(product_name = fct_reorder(product_name, n)) %>% 
  plot_ly(x = ~product_name, y = ~n, color = ~product_name, type = "bar", colors = "viridis")
```



